---
title: "Introduction to SA23204171"
author: "SA23204171"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SA23204171}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__SA23204171__ is a simple package that converts portfolio data into a specific 
from. Given a data frame of which each row containing the first 10 core stocks 
of a portfolio, convert it to a matrix with its rownames being the names of all 
core stocks in the data frame, and the rest of rows marking whether this core 
stock appears in the portfolio corresponding to its row in the original data frame 
with 1 and 0. Meanwhile there might be false data in some portfolios, and we 
find them and correct them.

## Convert a correct portfolio data frame

For simplicity we use the 26 letters as stock names to give the following 
example.

```{r}
# stock name
stock <- LETTERS
l <- list()
for(i in 1:10){
  # generate 10 portfolios
  l[[i]] <- sample(stock, 10)
}
# portfolio is a data frame with each row containing the 10 core stocks of a 
# portfolio. portfolio has no error data, because every stock appears at most 
# once in each row.
portfolio <- as.data.frame(rbind(l[[1]], l[[2]], l[[3]], l[[4]], l[[5]], l[[6]],
                                 l[[7]], l[[8]], l[[9]], l[[10]]))
# convert the data frame
library(SA23204171)
result <- convert(portfolio)
```

The output __result__ is a list. The first element _res_ is the converted 
matrix with each row corresponding to the portfolio in the data frame
__portfolio__, and if _res_[i, j] = 1, then stock j appears in the portfolio i.
Besides, the order of _res_'s rownames corresponds to the number of times of 
each stock appearing in all portfolios. Namely, the R code "colSums(result$res)"
gives a vector of descending order. The second element _data_ is the original data 
frame __portfolio__. The third element _mat.m_ is of no use to the user. The 
last element _correct_ tells whether the original data frame contains false data. 
If _correct_ is TRUE, then the original data frame contains no false data, FALSE
otherwise.

## Convert a portfolio data frame with error data

For simplicity we use the 26 letters as stock names to give the following 
example.

```{r}
# stock names
stock <- LETTERS
l <- list()
for(i in 1:10){
  # generate 10 portfolios
  l[[i]] <- sample(stock, 10)
}
# this portfolio contains false data, with a few stocks appearing more than once
# in the same portfolio
l[[1]][10] <- l[[1]][5]
l[[6]][8] <- l[[6]][2]
portfolio <- as.data.frame(rbind(l[[1]], l[[2]], l[[3]], l[[4]], l[[5]], l[[6]],
                                 l[[7]], l[[8]], l[[9]], l[[10]]))
# first use the function convert() to convert the data frame
library(SA23204171)
result <- convert(portfolio)
result$correct
# FALSE means there are errors in the original data, so we use correct.error() 
# to filter out these false portfolios and give the correct converted matrix.
# The error is apparent because there are "2" in the converted matrix.
new_result <- correct.error(result)
new_result
```

The output __new_result__ of the function correct.error() is a list. The first 
element is the correct matrix, and this time it contains only 8 rows, because 
the 1st and 6th portfolio have been filtered out. The second element provides a
check for whether this time the converted matrix is correct.
